MT Field Site Analysis Report

### 2024-04-05 qmd/projects/msu/toadflax/toadflax_report.qmd
updated locoweed field report

**Type:** This section has data organized by the four grouping variables - YT, DT, Natural, and Synthetic.

```{r boxplot data type, echo = F}
boxplot.data.type <-
  data %>%
    pivot_longer(-c(gc_file, plant_id, plant, type, day),
               names_to = "compound",
               values_to = "value") %>%
    group_by(type, compound) %>%
    mutate(count = n(),
           average = mean(value),
           sd = sd(value),
           se = (sd/sqrt(count))) %>%
    reframe(type, compound,
            average = mean(average),
            sd = mean(sd),
            se = mean(se)) %>%
  unique() 
```
```{r boxplot comparison category (original data), echo = F, fig.height = 20, fig.width = 20}
boxplot.data.type %>%
  mutate(type = factor(type, levels = c("DT", "YT", "Natural", "Synthetic"))) %>%
  ggplot(aes(x = type, y = average, fill = type)) +
  geom_bar(stat = "identity", alpha = 0.5) +
  geom_errorbar(aes(x = type,
                    ymin = average - se,
                    ymax = average + se),
                position = position_dodge(0.9),
                width = 0.2,
                alpha = 0.5) +
  labs(x = element_blank(),
       y = "VOC Concentration (ng/g/hr)") +
  theme(axis.text.x = element_text(angle = 45, 
                                    hjust = 1),
        legend.position = 'none',
        # legend.position = c(0.8,0.9),
        panel.background = element_rect(fill = "white"),
        axis.line = element_line(color = "black"),
        panel.grid.major.x = element_line(color = "#F2F2F2"),
        axis.text = element_text(size = 22),
        axis.title = element_text(size = 22),
        strip.text = element_text(size = 22)) +
  facet_wrap(~compound, 
             scales = "free_y",
             ncol = 3)

@@

```{r boxplot data plant, echo = F}
boxplot.data.plant <-
  data %>%
    pivot_longer(-c(gc_file, plant_id, plant, type, day),
               names_to = "compound",
               values_to = "value") %>%
    group_by(plant, compound) %>%
    mutate(count = n(),
           average = mean(value),
           sd = sd(value),
           se = (sd/sqrt(count))) %>%
    reframe(plant, compound,
            mean = mean(average),
            sd = mean(sd),
            se = mean(se)) %>%
  unique() %>%
  left_join(data %>%
              dplyr::select(plant, type),
            by = "plant",
            relationship = "many-to-many") %>%
  unique() %>%
  mutate(plant = factor(plant, 
                        levels = c("D6", "Y6", 
                                   "D6Y6", "Y6D6",
                                   "HBR", "RAD"))) %>%
  mutate(compound = factor(compound, levels = compound.order)) %>%
  na.omit()
```
```{r boxplot comparison plant (original data), echo = F, fig.height = 20, fig.width = 20}
boxplot.data.plant  %>%
  ggplot(aes(x = plant, y = mean, fill = type)) +
  geom_bar(stat = "identity", alpha = 0.5) +
  geom_errorbar(aes(x = plant,
                    ymin = mean - se,
                    ymax = mean + se),
                position = position_dodge(0.9),
                width = 0.2,
                alpha = 0.5) +
  labs(x = element_blank(),
       y = "VOC Concentration (ng/g/hr)") +
  theme(axis.text.x = element_text(angle = 45, 
                                    hjust = 1),
        legend.position = 'bottom',
        # legend.position = c(0.8,0.9),
        panel.background = element_rect(fill = "white"),
        axis.line = element_line(color = "black"),
        panel.grid.major.x = element_line(color = "#F2F2F2"),
        axis.text = element_text(size = 22),
        axis.title = element_text(size = 22),
        strip.text = element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.title = element_text(size = 22)) +
  facet_wrap(~compound, 
             scales = "free_y",
             ncol = 3)

>>>>

**Type:** This section has data organized by the four grouping variables - YT, DT, Natural, and Synthetic.
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

<div class="button-container">
  <a href="larger_boxplots.qmd">
    <button class="button">View Larger Boxplots</button>
  </a>

```{r boxplot data type, echo = F}
boxplot.data.type <-
  data %>%
    pivot_longer(-c(gc_file, plant_id, plant, type, day),
               names_to = "compound",
               values_to = "value") %>%
    group_by(type, compound) %>%
    mutate(count = n(),
           average = mean(value),
           sd = sd(value),
           se = (sd/sqrt(count))) %>%
    reframe(type, compound,
            average = mean(average),
            sd = mean(sd),
            se = mean(se)) %>%
  unique() 
```
```{r boxplot comparison category (original data), echo = F, fig.height = 20, fig.width = 20}
boxplot.data.type.plot <-
  boxplot.data.type %>%
  mutate(type = factor(type, levels = c("DT", "YT", "Natural", "Synthetic"))) %>%
  ggplot(aes(x = type, y = average, fill = type)) +
  geom_bar(stat = "identity", alpha = 0.5) +
  geom_errorbar(aes(x = type,
                    ymin = average - se,
                    ymax = average + se),
                position = position_dodge(0.9),
                width = 0.2,
                alpha = 0.5) +
  labs(x = element_blank(),
       y = "VOC Concentration (ng/g/hr)") +
  theme(axis.text.x = element_text(angle = 45, 
                                    hjust = 1),
        legend.position = 'none',
        panel.background = element_rect(fill = "white"),
        axis.line = element_line(color = "black"),
        panel.grid.major.x = element_line(color = "#F2F2F2")) +
  facet_wrap(~compound, 
             scales = "free_y",
             ncol = 3)

boxplot.data.type.plot +
  theme(axis.text = element_text(size = 22),
        axis.title = element_text(size = 22),
        strip.text = element_text(size = 22))

<div class="button-container">
  <a href="larger_boxplots.qmd">
    <button class="button">View Larger Boxplots</button>
  </a>

@@

```{r boxplot data plant, echo = F}
boxplot.data.plant <-
  data %>%
    pivot_longer(-c(gc_file, plant_id, plant, type, day),
               names_to = "compound",
               values_to = "value") %>%
    group_by(plant, compound) %>%
    mutate(count = n(),
           average = mean(value),
           sd = sd(value),
           se = (sd/sqrt(count))) %>%
    reframe(plant, compound,
            mean = mean(average),
            sd = mean(sd),
            se = mean(se)) %>%
  unique() %>%
  left_join(data %>%
              dplyr::select(plant, type),
            by = "plant",
            relationship = "many-to-many") %>%
  unique() %>%
  mutate(plant = factor(plant, 
                        levels = c("D6", "Y6", 
                                   "D6Y6", "Y6D6",
                                   "HBR", "RAD"))) %>%
  mutate(compound = factor(compound, levels = compound.order)) %>%
  na.omit()
```
```{r boxplot comparison plant (original data), echo = F, fig.height = 20, fig.width = 20}
boxplot.data.plant  %>%
  ggplot(aes(x = plant, y = mean, fill = type)) +
  geom_bar(stat = "identity", alpha = 0.5) +
  geom_errorbar(aes(x = plant,
                    ymin = mean - se,
                    ymax = mean + se),
                position = position_dodge(0.9),
                width = 0.2,
                alpha = 0.5) +
  labs(x = element_blank(),
       y = "VOC Concentration (ng/g/hr)") +
  facet_wrap(~compound, 
             scales = "free_y",
             ncol = 3) +
  theme(axis.text.x = element_text(angle = 45, 
                                    hjust = 1),
        legend.position = 'bottom',
        # legend.position = c(0.8,0.9),
        panel.background = element_rect(fill = "white"),
        axis.line = element_line(color = "black"),
        panel.grid.major.x = element_line(color = "#F2F2F2"),
        axis.text = element_text(size = 22),
        axis.title = element_text(size = 22),
        strip.text = element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.title = element_text(size = 22))

### 2024-04-05 qmd/projects/msu/wss/field_report.qmd
updated locoweed field report

<div class="image-container">
    <img src="img/field-sites/big-sandy-wide.jpg" alt="Your Image">
</div>

@@

```{r (raw) brome data, echo = F}
raw.2022 <- 
  read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/Field Sites/2022/2022 FS Stem Data (2).xlsx", sheet = "n.infested") %>%
  mutate(year = "2022") %>%
  rename("site" = site.cap)

raw.2023 <-
read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/Field Sites/2023/2023\ Field Site\ Data.xlsx", sheet = "n.infested") %>%
  mutate(year = "2023") 
```
```{r (stubble.####) stubble data, echo = F}
stubble.2023 <-
  read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/Field Sites/2023/2023\ Field Site\ Data.xlsx", 
           sheet = "stubble") %>%
  dplyr::select(-name) %>%
  na.omit() %>%
  mutate(year = "2023")

stubble.2022 <-
  read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/Field Sites/2022/2022 FS Stem Data (2).xlsx", 
             sheet = "stubble") %>%
  mutate(year = "2022")

@@

<div class="container">
  <img class="image" src="img/field-sites/nnns.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

@@

<div class="container">
  <img class="image" src="img/field-sites/gardiner.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

@@

<div class="container">
  <img class="image" src="img/field-sites/harvest.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

@@

<div class="container">
  <img class="image" src="img/field-sites/kolin.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

>>>>

<div class="image-container">
    <img src="../../../../img/field-sites/big-sandy-wide.jpg" alt="Your Image">
</div>

@@

```{r (raw) brome data, echo = F}
raw.2022 <- 
  read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/field Sites/2022/2022 FS Stem Data (2).xlsx", sheet = "n.infested") %>%
  mutate(year = "2022") %>%
  rename("site" = site.cap)

raw.2023 <-
read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/field Sites/2023/2023\ Field Site\ Data.xlsx", sheet = "n.infested") %>%
  mutate(year = "2023") 
```
```{r (stubble.####) stubble data, echo = F}
stubble.2023 <-
  read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/field Sites/2023/2023\ Field Site\ Data.xlsx", 
           sheet = "stubble") %>%
  dplyr::select(-name) %>%
  na.omit() %>%
  mutate(year = "2023")

stubble.2022 <-
  read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/field Sites/2022/2022 FS Stem Data (2).xlsx", 
             sheet = "stubble") %>%
  mutate(year = "2022")

@@

<div class="container">
  <img class="image" src="../../../../img/field-sites/nnns.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

@@

<div class="container">
  <img class="image" src="../../../../img/field-sites/gardiner.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

@@

<div class="container">
  <img class="image" src="../../../../img/field-sites/harvest.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

@@

<div class="container">
  <img class="image" src="../../../../img/field-sites/kolin.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>
